---
title: 'STAT 420 - Project Proposal'
authors: "Joshua Ceaser, Bryan Holcomb, Alejandro Pimentel (ap41)"
date: '07/19/2021'
output:
  html_document: 
    theme: readable
    toc: yes  
    code_folding: show
  pdf_document: default
urlcolor: cyan
editor_options: 
  chunk_output_type: console
---

```{css, echo=FALSE}
p, li, td {
  font-family: "Helvetica Neue", Helvetica, Arial, sans-serif;
}
```

```{r message=FALSE, warning=FALSE, class.source = 'fold-hide'}
library(knitr)
library(kableExtra)
library(dplyr)

format_numerics <- function(data, digits = 2, notation_threshold = 0.00001) {
  # make sure is a data.frame, then format
  if(!is.data.frame(data)){
    data <- as.data.frame(data)
  }  
  data %>% 
    mutate_if(
      is.numeric, 
      function(x) {
        if_else(
          abs(x) < notation_threshold, 
          formatC(x, digits = digits, format = "e"), 
          formatC(x, digits = digits, format = "f", drop0trailing = FALSE)
        )
      }
    )
}

gen_kable <- function(table_data, add_row_names = TRUE, caption = "", col_names = c(), row_names = c()) {
  f_data <- format_numerics(table_data) 
  if(length(col_names) != 0){
    colnames(f_data) <- col_names
  }
  if(length(row_names) != 0){
    rownames(f_data) <- row_names
  }  
  f_data %>%
  kable(., format = "html", row.names = add_row_names,
        caption = caption, escape = FALSE) %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                  full_width = F,
                  font_size = 14,
                  position = "center")
}
```


# Project Proposal

## Team members

Team Name: Team Texas, (aka The Normal Guys)

- Joshua Ceaser **(your id here)**
- Bryan Holcomb **(your id here)**
- Alejandro Pimentel **(ap41)**

## Project Title

**Quality metrics for water potability**

## Description of the data file.

File name: **water_potability.csv**

```{r message=FALSE, warning=FALSE}
library(readr)
water_potability <- read_csv("./water_potability.csv")
```

Number of variables: **`r dim(water_potability)[2]`**

Number of observations: **`r dim(water_potability)[1]`**

```{r, class.source = 'fold-hide'}
gen_kable(colnames(water_potability), 
          col_names = c("Variable Name"),
          caption = "List of variables")
```

## Background information

(Needs work)

## Statement of interest

(Needs work)

## Data load proof

Data has been load above in variable `water_potability`.

Here we take a look at a few of the `response` values. Note that `Potability` is binary response variable, so we intend to use `Logistic Regression`.

```{r}
head(water_potability[, "Potability"])
```

